### 2019-10-09 tim-lucas-model-ensembles.tex
Continue messing with table.

\begin{table}
\caption{Machine learning model results and means of fitted parameters (i.e.\thinspace model weights) across cross-validation folds of the machine learning predictions only model. }
\centering
\small
\begin{tabular}{ll|rrrr}
     Country          & Model &      RMSE & $\beta_l $ &   $\beta_g$   &  $\beta_{g+l}$                                 \\ \hline
Madagascar & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Madagascar & RF\textsubscript{g} &  0.169 & - &&\\
Madagascar & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Madagascar & GBM\textsubscript{g} &  0.178& - &&\\
Madagascar & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Madagascar & enet\textsubscript{g} & 0.233 & - &&\\
Madagascar & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Madagascar & nnet\textsubscript{g} &  0.220 & - &&\\
Madagascar & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Madagascar & ppr\textsubscript{g} & 0.205 &  &&\vspace{0.3cm}\\ 
Colombia & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Colombia & RF\textsubscript{g} &  & - &&\\
Colombia & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Colombia & GBM\textsubscript{g} &  & - &&\\
Colombia & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Colombia & enet\textsubscript{g} &  & - &&\\
Colombia & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Colombia & nnet\textsubscript{g} &  & - &&\\
Colombia & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Colombia & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Senegal & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Senegal & RF\textsubscript{g} &  & - &&\\
Senegal & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Senegal & GBM\textsubscript{g} &  & - &&\\
Senegal & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Senegal & enet\textsubscript{g} &  & - &&\\
Senegal & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Senegal & nnet\textsubscript{g} &  & - &&\\
Senegal & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Senegal & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Indonesia & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Indonesia & RF\textsubscript{g} &  & - &&\\
Indonesia & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Indonesia & GBM\textsubscript{g} &  & - &&\\
Indonesia & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Indonesia & enet\textsubscript{g} &  & - &&\\
Indonesia & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Indonesia & nnet\textsubscript{g} &  & - &&\\
Indonesia & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Indonesia & ppr\textsubscript{g} &  &  &&\\
\end{tabular}
\label{t:mlresults}
\end{table}

>>>>

\begin{table}
\caption{Machine learning model results and means of fitted parameters (i.e.\thinspace model weights) across cross-validation folds of the machine learning predictions only model. }
\centering
\small
\begin{tabular}{ll|rr}
     Country          & Model &      RMSE & $\beta$ \\ \hline
Madagascar & RF\textsubscript{l} & 0.100 & 0.337 \\
Madagascar & GBM\textsubscript{l} & 0.105 & 0.450 \\
Madagascar & enet\textsubscript{l} & 0.116 & 0.326 \\
Madagascar & nnet\textsubscript{l} & 0.113 & 0.031 \\
Madagascar & ppr\textsubscript{l} & 0.109 & -0.233\vspace{0.3cm}\\ 
Madagascar & RF\textsubscript{g} &  0.169 & - \\
Madagascar & GBM\textsubscript{g} &  0.178& - \\
Madagascar & enet\textsubscript{g} & 0.233 & - \\
Madagascar & nnet\textsubscript{g} &  0.220 & - \\
Madagascar & ppr\textsubscript{g} & 0.205 &   \vspace{0.3cm}\\
Colombia & RF\textsubscript{l} & 0.100 & 0.337 \\
Colombia & GBM\textsubscript{l} & 0.109 & 0.450  \\
Colombia & enet\textsubscript{l} & 0.100 & 0.326 \\
Colombia & nnet\textsubscript{l} & 0.113 & 0.031 \\
Colombia & ppr\textsubscript{l} & 0.110 & -0.233\vspace{0.3cm}\\
Colombia & RF\textsubscript{g} & 0.169 & -\\
Colombia & GBM\textsubscript{g} & 0.178 & - \\
Colombia & enet\textsubscript{g} & 0.233 & - \\
Colombia & nnet\textsubscript{g} & 0.220 & - \\
Colombia & ppr\textsubscript{g} & 0.205 & \vspace{0.3cm}\\ 
Senegal & RF\textsubscript{l} & 0.100 & 0.337 \\
Senegal & GBM\textsubscript{l} & 0.109 & 0.450 \\
Senegal & enet\textsubscript{l} & 0.100 & 0.326 \\
Senegal & nnet\textsubscript{l} & 0.113 & 0.031 \\
Senegal & ppr\textsubscript{l} & 0.110 & -0.233\vspace{0.3cm}\\
Senegal & RF\textsubscript{g} & 0.169 & \\
Senegal & GBM\textsubscript{g} & 0.178 & - \\
Senegal & enet\textsubscript{g} & 0.233 & - \\
Senegal & nnet\textsubscript{g} & 0.220 & - \\
Senegal & ppr\textsubscript{g} & 0.205 & \vspace{0.3cm} \\ 
Indonesia & RF\textsubscript{l} & 0.100 & 0.337 \\
Indonesia & GBM\textsubscript{l} & 0.109 & 0.450 \\
Indonesia & enet\textsubscript{l} & 0.100 & 0.326\\
Indonesia & nnet\textsubscript{l} & 0.113 & 0.031 \\
Indonesia & ppr\textsubscript{l} & 0.110 & -0.233\vspace{0.3cm}\\
Indonesia & RF\textsubscript{g} & 0.169 & \\
Indonesia & GBM\textsubscript{g} & 0.178 & \\
Indonesia & enet\textsubscript{g} &0.233  &\\
Indonesia & nnet\textsubscript{g} &0.220  &\\
Indonesia & ppr\textsubscript{g} & 0.205 &  \\
\end{tabular}
\label{t:mlresults}
\end{table}
